Draft Exploration

### 2020-04-27 draft_exploration.Rmd
signing probability by round and year function in Rmd

>>>>

```{r}

hs_sign_by_round <- function(startyear, endyear = startyear + 4) {

by_round <- master %>%
  filter(source == "H") %>%
  filter(year >= startyear & year <= endyear) %>%
  mutate(half_decade = as.factor(ifelse(year %in% 1990:1994, 1990,
                                 ifelse(year %in% 1995:1999, 1995,
                                        ifelse(year %in% 2000:2004, 2000,
                                               ifelse(year %in% 2005:2009, 2005,
                                                      ifelse(year %in% 2010:2014, 2010, 
                                                             ifelse(year %in% 2015:2019, 2015, NA)))))))) %>%
  mutate(signed_numeric = ifelse(signed == "Y", 1, 0)) %>%
  group_by(draft_round, half_decade) %>%
  summarize(percent_signed = sum(signed_numeric) / n(),
            drafted = n(),
            signed = sum(signed_numeric)) %>%
  mutate(percent_signed = ifelse(half_decade == 2010 & draft_round > 40, NA, percent_signed))

by_round %>%
  ggplot(aes(draft_round, percent_signed)) +
  geom_smooth(formula = y~x+x^2, aes(group = half_decade, color = half_decade), se = FALSE, size = 1) +
  theme_light()

hs_sign_by_round(startyear = 1990, endyear = 2019)

```{r}
draft_2019 <- master %>%
  filter(year == 2019) %>%
  filter(signed == "N") %>%
  arrange(draft_round)

signed_by_year <- master %>%
  mutate(signed_numeric = ifelse(signed == "Y", 1, 0)) %>%
  group_by(year) %>%
  summarize(percent_signed = sum(signed_numeric) / n(),
            drafted = n(),
            signed = sum(signed_numeric))

signed_by_year %>%
  ggplot(aes(year, percent_signed)) +
  geom_point(color = "dodgerBlue4") +
  geom_line(color = "dodgerBlue") +
  theme_light() +
  labs(
    x = "Year",
    y = "Percent of Picks Signed"
  )

signed_by_year_hs <- master %>%
  filter(source == "H" & draft_round >= 20 & draft_round <= 40) %>%
  mutate(signed_numeric = ifelse(signed == "Y", 1, 0)) %>%
  group_by(year) %>%
  summarize(percent_signed = sum(signed_numeric) / n(),
            drafted = n(),
            signed = sum(signed_numeric))

signed_by_year_hs %>%
  ggplot(aes(year, percent_signed)) +
  geom_point(color = "dodgerBlue4") +
  geom_line(color = "dodgerBlue") +
  theme_light() +
  labs(
    x = "Year",
    y = "Percent of Picks Signed",
    title = "Signability of High School Picks Over Time"
  )
```
